### 2019-08-23 reports/thesis/chapters/5_inference.tex
In inference, make comment on initial value in DefectExample

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_imageClean.eps}
        \caption{Uncontaminated}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_imageContaminated.eps}
        \caption{Contaminated}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_EmpiricalNullFilternullStd.eps}
        \caption{Filtered}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_EmpiricalNullFilternullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
    }
  \caption{A $256 \times 256$ Gaussian image with a \emph{square} defect is shown in a). The image was contaminated in b) and then filtered with kernel radius \emph{40} in c). Defected pixels have the distribution $\normal(3,1)$. The speckle defect has density $\pi_1 = 0.1$. The line defect is 5 pixels thick. The square defect is $30\times 30$ pixels in size. The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. In a) and c), highlighted in red are pixels tested as positive at the 5\% FDR level.}
  \label{fig:inference_defectSquare2Example}
\end{figure}

@@

>>>>

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_imageClean.eps}
        \caption{Uncontaminated}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_imageContaminated.eps}
        \caption{Contaminated}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_EmpiricalNullFilterimageFiltered.eps}
        \caption{Filtered}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_EmpiricalNullFilternullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
    }
  \caption{A $256 \times 256$ Gaussian image with a \emph{square} defect is shown in a). The image was contaminated in b) and then filtered with kernel radius \emph{40} in c). Defected pixels have the distribution $\normal(3,1)$. The speckle defect has density $\pi_1 = 0.1$. The line defect is 5 pixels thick. The square defect is $30\times 30$ pixels in size. The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. In a) and c), highlighted in red are pixels tested as positive at the 5\% FDR level.}
  \label{fig:inference_defectSquare2Example}
\end{figure}

@@

The empirical null mean in Figure \ref{fig:inference_defectSquareExample} demonstrates the multi-thread nature of the implementation of the empirical null filter. It can be seen that there are horizontal streaks where the defect is. This is the result of each thread filtering a row each and jumping from one mode, the null, to the other, the non-null, at different times. The horizontal streaks can be removed by using more initial values so that the Newton-Raphson method can pin point which mode is greater.
